---
title: "Which screen kill runs?"
output: html_notebook
---

First thing is first, let's load the needed libraries and the data

```{r}
library(dplyr)
library(ggplot2)

room_data <- read.csv("../data/fixed_room_data.csv")
room_order <- read.csv("../data/unique_room_list_double_hundo_fixed_with_index.csv", header = FALSE, col.names = c('Number','Room'))
```


Let's start with a data frame were we calculate the number of times each room is entered and each time the run ends on the run.

```{r}
my_count <- room_data %>%
  group_by(Room) %>%
  summarise(times_killed_run = sum(is.na(Duration)), times_entered = length (Duration) )
```

So here's a bit of magic you need to make sure stuff is displayed in right order.  I'll need to fix this later thougn because the order might not be 100% correct.

```{r}
rooms_ordered <- merge(my_count, room_order, by= "Room")
rooms_ordered$Room <- 
  reorder(rooms_ordered$Room, rooms_ordered$Number)
```

And let's make a first go at ploting this stuff up.
```{r}
ggplot(rooms_ordered, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred')
```

The first thing to fix here is that there are WAY too many x-labels.  

```{r}
ggplot(rooms_ordered, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(name="Room Number",limits=c('1OH81
', '3DG81', '2OD71'))
```
 Ok so that didn't really work like I thought it might, it filters points.  Now let's try soemthing else
 
```{r}
ggplot(rooms_ordered, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  theme(axis.text.x = element_blank(),axis.ticks = element_blank())
```


Ok that gets rid of the Room numbers which I suppose is better.   Let's try with our truncated list again

```{r}
ggplot(rooms_ordered, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=c('1OH81', '3DG81', '2OD71'))
```
Ok great that works.  Now let's just make a list of all those rooms to pick

```{r}
rooms_to_display = c('1OH81', '3DG81', '2OD71', '4DF81','3OF61', '1DF81', 
                     '4OH41', ' 5DF71')
```

```{r}
ggplot(rooms_ordered, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=rooms_to_display)
```


Maybe just trying the first room each overworld and include a text rotation

```{r}
rooms_to_display = c('1OH81', '2OD71', '3OF61', '4OH41', '5OL11', 
                     '6OM41', '7OC51', '8OC31', '9ON71')
ggplot(rooms_ordered, aes(y=times_entered,x=Room)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=rooms_to_display) +
  theme(axis.text.x = element_text(angle = 65, hjust =1))
```

Ok now let's try some themes

```{r}
rooms_to_display = c('1OH81', '2OD71', '3OF61', '4OH41', '5OL11', 
                     '6OM41', '7OC51', '8OC31', '9ON71')
ggplot(rooms_ordered, aes(y=times_entered,x=Room)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=rooms_to_display) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 65, hjust =1)) + 
  ylab('number of times room entered') + 
  coord_cartesian(xlim = c(0,25)) + 
  xlab('Room')
```
Okay well let's take look at Room that killed runs

```{r}
rooms_to_display = c('1OH81', '2OD71', '3OF61', '4OH41', '5OL11', 
                     '6OM41', '7OC51', '8OC31', '9ON71')
ggplot(rooms_ordered, aes(y=times_killed_run,x=Room)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=rooms_to_display) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 65, hjust =1)) + 
  ylab('number of times room killed run') + 
  #coord_cartesian(xlim = c(0,25)) + 
  xlab('Room')
```

```{r}
rooms_to_display = c('1OH81', '2OD71', '3OF61', '4OH41', '5OL11', 
                     '6OM41', '7OC51', '8OC31', '9ON71')
ggplot(rooms_ordered, aes(y=times_killed_run/times_entered,x=Room)) + 
  geom_point(color = 'darkred') +
  #scale_x_discrete(breaks=rooms_to_display) +
  theme_minimal() + 
  theme(axis.text.x = element_text(angle = 65, hjust =1)) + 
  ylab('percent of times room killed run') + 
  coord_cartesian(ylim = c(0,0.4), xlim = c(1,50)) + 
  xlab('Room')
```

