---
title: "Which screen kill runs?"
output: html_notebook
---

First thing is first, let's load the needed libraries and the data

```{r}
library(dplyr)
library(ggplot2)

room_data <- read.csv("../data/fixed_room_data.csv")
room_order <- read.csv("../data/unique_room_list_double_hundo_fixed_with_index.csv", header = FALSE, col.names = c('Number','Room'))
```


Let's start with a data frame were we calculate the number of times each room is entered and each time the run ends on the run.

```{r}
my_count <- room_data %>%
  group_by(Room) %>%
  summarise(times_killed_run = sum(is.na(Duration)), times_entered = length (Duration) )
```

So here's a bit of magic you need to make sure stuff is displayed in right order.  I'll need to fix this later thougn because the order might not be 100% correct.

```{r}

my_count$Room <- 
  reorder(my_count$Room,desc(my_count$times_entered))
```

And let's make a first go at ploting this stuff up.
```{r}
ggplot(my_count, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred')
```

The first thing to fix here is that there are WAY too many x-labels.  

```{r}
ggplot(my_count, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(name="Room Number",limits=c('1OH81
', '3DG81', '2OD71'))
```
 Ok so that didn't really work like I thought it might, it filters points.  Now let's try soemthing else
 
```{r}
ggplot(my_count, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  theme(axis.text.x = element_blank(),axis.ticks = element_blank())
```


Ok that gets rid of the Room numbers which I suppose is better.   Let's try with our truncated list again

```{r}
ggplot(my_count, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=c('1OH81', '3DG81', '2OD71'))
```
Ok great that works.  Now let's just make a list of all those rooms to pick

```{r}
rooms_to_display = c('1OH81', '3DG81', '2OD71', '4DF81','3OF61', '1DF81', 
                     '4OH41', ' 5DF71')
```

```{r}
ggplot(my_count, aes(y=times_entered,x=Room, f)) + 
  geom_point(color = 'darkred') +
  scale_x_discrete(breaks=rooms_to_display)
```

Ok I just noticed some weird ordering stuff.  I definitely need to fix that.

Ok i'm back now and I have a few minutes.  I think the first thing to do is to fix the order stuff.

```{r}
my_count$Room[70:72]
my_count$times_entered[70:72]
```

Ok room 5OP41 appears out of place.  It may appear TWICE in 'unique_room_list_double_hundo.csv'  

CONFIRMED it does appear twice.  Ok that will require a fix.

I still need a function to play the room...

Ok so the room is actually a quick heart grab and it also apears to have never killed a run.  Interestingly, Dungeon 2 has NEVER killed a run in my data.

TODO:

- CHECK REST OF ROOMS
- FIX YOUR ROOM LIST
- CREATE FUNCTION INPUT ROOM_ID OUTPUT ROOM NUMBER
- CREATE FUNCTION INPUT ROOM_ID OUTPUT PICTURE OF ROOM


this shows the for each run where 5OP41 is present, it's in the data twice
```{r}
room_data %>%
  filter(room_data$Room == '5OP41') %>%
  count(Run_Man) %>%
  summarise(min(n))
```

Create a list of rooms to filter

```{r}
runs2filter <- room_data %>%
  filter(Room == '5OP41') %>%
  distinct(Run_Man)
```

For each room to filter select '5OP41' and keep the one with older abs time

```{r}
for (run in runs2filter)
{
  rooms <- room_data %>%
    filter(Run_Man == run) %>%
    filter(Room == '5OP41') 
  print(paste(run))
}
```
 ok let's try to get this to work once okay

Is there something weird with 8450 and 6133?

```{r}
run = 6182
room <- room_data %>%
  filter(Run_Man == run) %>%
  filter(Room == '5OP41')
print(room)

run = 6133
room <- room_data %>%
  filter(Run_Man == run) %>%
  filter(Room == '5OP41')
print(room)

run = 8450
room <- room_data %>%
  filter(Run_Man == run) %>%
  filter(Room == '5OP41')
print(room)
```



```{r}
run = 6133
room <- room_data %>%
  filter(Run_Man == run) %>%
  filter(Room == '5OP41')
  
max_time <- max(room$Abs_time)

room2 <- room %>%
  filter(Abs_time == max_time) %>%
  mutate(Room = '5OP42')
  
```

Okay so that changes a SINGLE room ! Phew


Create an empty column onto rooms2filter
```{r}
runs2filter$keys<- -1
```


```{r}
run = 8450
room <- room_data %>%
  filter(Run_Man == run) %>%
  filter(Room == '5OP41')

max_time <- max(room$Abs_time)
print(max_time)

room2 <-room %>%
  filter(Abs_time == max_time) %>%
  .$AKey

print(room2)
runs2filter$keys[runs2filter$Run_Man == run] <- room2

print(runs2filter)
```

Let's try it for all of them

```{r}
for (run in runs2filter$Run_Man)
{
  
  room <- room_data %>%
    filter(Run_Man == run) %>%
    filter(Room == '5OP41')
  
  max_time <- max(room$Abs_time)
  
  
  room2 <-room %>%
    filter(Abs_time == max_time) %>%
    .$AKey
  
  
  runs2filter$keys[runs2filter$Run_Man == run] <- room2
  
}
```
That worked! Hurray!!!

Let's try fixing `room_data`

```{r}
room_data_fixed <- room_data
#add factor
room_list <- levels(room_data_fixed$Room)
new_room_list <- c(room_list, '5OP42') 
levels(room_data_fixed$Room) = new_room_list
key = 116

room_data_fixed$Room[room_data_fixed$AKey == key] <- '5OP42'
```


```{r}
room_data_fixed <- room_data
room_list <- levels(room_data_fixed$Room)
new_room_list <- c(room_list, '5OP42') 
levels(room_data_fixed$Room) = new_room_list
for (key in runs2filter$keys){
  
  room_data_fixed$Room[room_data_fixed$AKey == key] <- '5OP42'
  
}
```


Wow okay that worked
Next to do is the save 'room_data_fixed' to a csv and restructure this file.
