---
title: "Create_histogram_of_Durations"
output: html_notebook
---

So what you want to do here is make a function the given a room number will output a histogram of durations of rooms.  This objective may change but lets look at bins, etc before making up my mind here.

first thing, lets load data and some packages

```{r}
library(dplyr)
library(ggplot2)
library(grid)
library(gridExtra)

room_data <- read.csv("../data/fixed_room_data.csv")
room_order <- read.csv("../data/unique_room_list_double_hundo_with_index.csv", header = FALSE, col.names = c('Number','Room'))
```

```{r}
create_hist <- function(RoomNumber) {
  # filter out the data you need
  durations_for_rooms <- room_data %>%
    filter(Room == RoomNumber) %>%
    na.omit() 
  
  # create your super cool label
  the_label = paste("Duration of", RoomNumber ,"(seconds)")
  
  
  # make your gg plot
  ggplot(durations_for_rooms, aes(x = Duration) ) + 
    geom_histogram(binwidth = 0.1,
                 fill = 'red',
                 position="identity",
                 alpha= 0.4) +
    xlab(the_label)
}

# call the function
create_hist('3DF71')
```

So I think the "agile" thing to do here is to put this in a shiny app with a dropdown menu of the rooms.  It would be pretty cool.

I think this is a great template to start from `http://shiny.rstudio.com/gallery/telephones-by-region.html`

We need a unique list of room
```{r}
room_list <- unique(room_data$Room)
```

